\documentclass[a4paper,12pt]{jsarticle}
\usepackage[T1]{fontenc}
\usepackage{newenum}
\usepackage{epsfig}

\usepackage{enumerate}

\usepackage{graphicx}
\newcommand{\figdir}{../figures}

% theorem
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\newtheorem*{cooperativepatrollingproblem}{{\patProb}}
\newtheorem*{timeSpecifiedCooperativePatrollingProblem}{時刻指定{\patProb}}
\newtheorem*{timeSpecifiedCooperativePatrollingProblemDecision}{時刻指定協力警邏判定問題}
\newtheorem*{timeSpecifiedProblemOnLine}{時刻指定線分警邏問題}
\newtheorem*{timeSpecifiedProblemOnLineSubProb}{副問題}
\newtheorem*{greedyAlgorithmForTimeSpecifiedProblemOnLine}{貪欲アルゴリズム}


 % Tikz
	\usepackage[dvipdfmx,svgnames]{xcolor}%tikzパッケージよりも前に読み込みます。
	\usepackage{tikz}%（これで，pgf と pgffor も読み込まれます。）
%%% color %%%
	% \usepackage[dvipdfmx]{color}    % 色付き文字
	\definecolor{mygreen}{rgb}{0, 0.6, 0} % R(赤),G(緑),B(青)
	\definecolor{myorange}{rgb}{0.8, 0.4, 0} % R(赤),G(緑),B(青)
	\newcommand{\black}      [1] {{\textcolor{black}{#1}}}
	\newcommand{\red}        [1] {{\textcolor{red}{#1}}}
	\newcommand{\blue}       [1] {{\textcolor{blue}{#1}}}
	\newcommand{\green}      [1] {{\textcolor{mygreen}{#1}}}
	\newcommand{\orange}     [1] {{\textcolor{myorange}{#1}}}

\input{macros.tex}


\title{複数の巡査の協力による指定地点の警邏について\\
	{\normalsize Collaborative Patrolling of Designated Points on Graphs}}
\author{
		河村 彰星 \\ Akitoshi Kawamura \and
		能城 秀彬 \\ Hideaki Noshiro
	}
%% 	\affliate{
%% 		東京大学総合文化研究科 \\
%% 		The University of Tokyo, Graduate School of Arts and Sciences
%% }






\begin{document}

\maketitle

%\input{abstract_jp.tex}


\input{./1_Introduction.tex}
\input{./2_Line_1.tex}
\input{./2_Line_2.tex}
\input{./3_Star.tex}
\input{./4_Unit.tex}


\begin{thebibliography}{1}

%\bibitem{agrawal2004primes}
%M. Agrawal, N. Kayal, and N. Saxena.
%\newblock Primes is in P.
%\newblock {\em Annals of Mathematics}, 160(2), pp. 781--793, 2004.

\bibitem{chen2013fence}
K.~Chen, A.~Dumitrescu, and A.~Ghosh.
\newblock On fence patrolling by mobile agents.
\newblock In {\it Proc.\ 25th Canadian Conference on Computational Geometry} (CCCG), 2013.


%\bibitem{coene2013balancing}
%S.~Coene, C.~Filippi, F.\,C.\,R. Spieksma, and E.~Stevanato.
%\newblock Balancing profits and costs on trees.
%\newblock {\em Networks}, 61(3), pp.~200--211, 2013.


\bibitem{coene2011charlemagne}
S.~Coene, F.\,C.\,R.~Spieksma, and G.\,J. Woeginger.
\newblock Charlemagne's challenge: the periodic latency problem.
\newblock {\em Operations research}, 59(3), pp.~674--683, 2011.


\bibitem{czyzowicz2011boundary}
J.~Czyzowicz, L.~G{\k{a}}sieniec, A.~Kosowski, and E.~Kranakis.
\newblock Boundary patrolling by mobile agents with distinct maximal speeds.
\newblock In {\it Proc.\ 19th Annual European Symposium on Algorithms} (ESA), LNCS~6942, pp.~701--712, 2011. 


%\bibitem{dusart1999k}
%P.~Dusart.
%\newblock The $k$th prime is greater than $k (\ln k + \ln \ln k - 1)$ for $k \geq 2$.
%\newblock {\em Mathematics of Computation}, 68, pp.~411--415, 1999.


\bibitem{kawamura2015simple}
A.~Kawamura and M.~Soejima.
\newblock Simple strategies versus optimal schedules in multi-agent patrolling.
\newblock In \emph{Proc.\ Ninth International Conference on Algorithms and Complexity} (CIAC), LNCS~9079, pp.~261--273, 2015.

\end{thebibliography}



\end{document}
