%%
%% 研究報告用スイッチ
%% [techrep]
%%
%% 欧文表記無しのスイッチ(etitle,jkeyword,eabstract,ekeywordは任意)
%% [noauthor]
%%

\documentclass[submit,techrep]{ipsj}
%\documentclass[submit,techrep,noauthor]{ipsj}

\usepackage[T1]{fontenc}

	\usepackage[dvipdfmx]{graphicx}

%\usepackage[dvips]{graphicx}
\usepackage{latexsym}


	\usepackage{enumerate}

% theorem
	\usepackage{amsmath,amssymb}
	\usepackage{amsthm}

 % Tikz
	\usepackage[dvipdfmx,svgnames]{xcolor}%tikzパッケージよりも前に読み込みます。
	\usepackage{tikz}%（これで，pgf と pgffor も読み込まれます。）
%%% color %%%
	% \usepackage[dvipdfmx]{color}    % 色付き文字
	\definecolor{mygreen}{rgb}{0, 0.6, 0} % R(赤),G(緑),B(青)
	\definecolor{myorange}{rgb}{0.8, 0.4, 0} % R(赤),G(緑),B(青)
	\newcommand{\black}      [1] {{\textcolor{black}{#1}}}
	\newcommand{\red}        [1] {{\textcolor{red}{#1}}}
	\newcommand{\blue}       [1] {{\textcolor{blue}{#1}}}
	\newcommand{\green}      [1] {{\textcolor{mygreen}{#1}}}
	\newcommand{\orange}     [1] {{\textcolor{myorange}{#1}}}




\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{巻数}{57
}%vol53=2012
\setcounter{号数}{10}
\setcounter{page}{1}


	\input{macros.tex}


\begin{document}

\title{複数の巡査による指定地点の警邏について}


\etitle{Patrolling designated points on graphs}

\affiliate{UT}{東京大学}


%\paffiliate{UT}{東京大学\\
%University of Tokyo}

\author{河村 彰星}{Akitoshi Kawamura}{UT}[kawamura@graco.c.u-tokyo.ac.jp]
\author{能城 秀彬}{Hideaki Noshiro}{UT}[noshiro.pf@gmail.com]


\input{abstract_jp.tex}



\maketitle


\input{body.tex}
\input{memo.tex}

\begin{acknowledgment}
  本研究は旭硝子財団および科研費新学術領域「計算限界解明」の助成を受けて行われた。
\end{acknowledgment}

% \bibliographystyle{jplain}
% \bibliography{bibsample}

\begin{thebibliography}{1}

\bibitem{agrawal2004primes}
M. Agrawal, N. Kayal, and N. Saxena.
\newblock Primes is in P.
\newblock {\em Annals of Mathematics}, 160(2), pp. 781--793, 2004.

\bibitem{chen2013fence}
K.~Chen, A.~Dumitrescu, and A.~Ghosh.
\newblock On fence patrolling by mobile agents.
\newblock In {\em CCCG}, 2013.

\bibitem{coene2013balancing}
S.~Coene, C.~Filippi, F.\,C.\,R. Spieksma, and E.~Stevanato.
\newblock Balancing profits and costs on trees.
\newblock {\em Networks}, 61(3), pp.~200--211, 2013.

\bibitem{coene2011charlemagne}
S.~Coene, F.\,C.\,R.~Spieksma, and G.\,J. Woeginger.
\newblock Charlemagne's challenge: the periodic latency problem.
\newblock {\em Operations research}, 59(3), pp.~674--683, 2011.

\bibitem{czyzowicz2011boundary}
J.~Czyzowicz, L.~G{\k{a}}sieniec, A.~Kosowski, and E.~Kranakis.
\newblock Boundary patrolling by mobile agents with distinct maximal speeds.
\newblock In {\em European Symposium on Algorithms}, pp.~701--712. Springer,
  2011.

\bibitem{dusart1999k}
P.~Dusart.
\newblock The $k$th prime is greater than $k (\ln k + \ln \ln k - 1)$ for $k \geq 2$.
\newblock {\em Mathematics of Computation}, 68, pp.~411--415, 1999.

\bibitem{kawamura2015simple}
A.~Kawamura and M.~Soejima.
\newblock Simple strategies versus optimal schedules in multi-agent patrolling.
\newblock In {\em International Conference on Algorithms and Complexity}, pp.
  261--273. Springer, 2015.

\end{thebibliography}


\end{document}
